---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-"
)
options(knitr.table.format = 'markdown')
```

# mmetrics

[![Travis-CI Build Status](https://api.travis-ci.com/shinichi-takayanagi/mmetrics.svg?branch=master)](https://travis-ci.com/shinichi-takayanagi/mmetrics) 
[![CRAN_Status_Badge](https://www.r-pkg.org/badges/version/mmetrics)](https://cran.r-project.org/package=mmetrics)
[![codecov](https://codecov.io/github/shinichi-takayanagi/mmetrics/branch/master/graphs/badge.svg)](https://codecov.io/github/shinichi-takayanagi/mmetrics) 
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)

## Installation

You can install the released version of {mmetrics} from CRAN with:

```r
install.packages("mmetrics")
```

Or install the development version from github with:

```r
# install.packages("remotes")
remotes::install_github("shinichi-takayanagi/mmetrics")
```

## Example
### Create Dummy data
First, we create dummy data for this example.
```{r}
# Dummy data
df <- data.frame(
  gender = rep(c("M", "F"), 5),
  age = (1:10)*10,
  cost = c(51:60),
  impression = c(101:110),
  click = c(0:9)*3,
  conversion = c(0:9)
)

head(df)
```

### Define metrics
As a next step, we define metrics to evaluate using `mmetrics::define`. 
```{r}
# Example metrics
metrics <- mmetrics::define(
  cost = sum(cost),
  ctr  = sum(click)/sum(impression)
)
```

### Just call `mmetrics::add()` !
Call `mmetrics::add()` with grouping key (here `gender`) then we will get new `data.frame` with defined metrics.
```{r}
mmetrics::add(df, gender, metrics = metrics)
```

## More examples

- As a first step, see the vignettes [Introduction to {mmetrics} package](https://shinichi-takayanagi.github.io/mmetrics/articles/introduction.html)
