---
title: "Introduction to {mmetrics} package"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to {mmetrics} package}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```


This vignette shows you how to use `{mmetrics}` package.

## Create Dummy Data

First, we create dummy data for this example.
```{r}
# Dummy data
df <- data.frame(
  gender = rep(c("M", "F"), 5),
  age = (1:10)*10,
  cost = c(51:60),
  impression = c(101:110),
  click = c(0:9)*3,
  conversion = c(0:9)
)

head(df)
```

## Define metrics
As a next step, we define metrics to evaluate using `mmetrics::define`. 
```{r}
# Example metrics
metrics <- mmetrics::define(
  cost = sum(cost),
  ctr  = sum(click)/sum(impression)
)
```

## How to use mmetrics::add() 

### mmetrics::add() with sigle grouping key
Call `mmetrics::add()` with grouping key (here `gender`) then we will get new `data.frame` with defined metrics.
```{r}
mmetrics::add(df, gender, metrics = metrics)
```

### mmetrics::add() with multiple grouping keys
We can also use multiple grouping keys.
```{r}
mmetrics::add(df, gender, age, metrics = metrics)
```

### mmetrics::add() without any grouping keys
If we do not specify any grouping keys, `mmetrics::add()` summarize all data as a default option.
```{r}
mmetrics::add(df, metrics = metrics)
```

If we want to `mmetrics::add()` behave like `dplyr::mutate()` use `mmetrics::disaggregate()`.
```{r}
metrics_disaggregated <- disaggregate(metrics)
mmetrics::add(df, metrics = metrics_disaggregated, summarize = FALSE)
```

`mmetrics::disaggregate()` remove *the first aggregation function* for the argument and return disaggregated metrics.
```{r}
disaggregate(metrics)
```

Using `mmetrics::disaggregate()`, we do not need to re-define metrics for `dplyr::mutate()`.


## gmutate() and gsummarize()

`mmetrics::add()` is a just wrapper function for `mmetrics::gmutate()` and `mmetrics::gsummarize()`.
We can use these functions directly instead of `mmetrics::add()`.
