---
title: "Introduction to {mmetrics} package"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to {mmetrics} package}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Introduction
Are you boring of repeated tabulation work? This package is for you.
With this package, you can reuse metrics which you define and easily do tabulation work on different analysis axes.
Focus on more productive things with this package! Have a wonderful life!

## Load Dummy Data

First, we load dummy data from {mmetrics} package for this example.
```{r}
# Load dummy data
df <- mmetrics::dummy_data
df
```

## Define metrics
As a next step, we define metrics to evaluate using `mmetrics::define`. 
```{r}
# Example metrics
metrics <- mmetrics::define(
  cost = sum(cost),
  ctr  = sum(click)/sum(impression)
)
```

## How to use mmetrics::add() 

### mmetrics::add() with sigle grouping key

Call `mmetrics::add()` with grouping key (here `gender`) then we will get new `data.frame` with defined metrics.
```{r}
mmetrics::add(df, gender, metrics = metrics)
```

### mmetrics::add() with multiple grouping keys
We can also use multiple grouping keys.
```{r}
mmetrics::add(df, gender, age, metrics = metrics)
```

### mmetrics::add() without any grouping keys
If we do not specify any grouping keys, `mmetrics::add()` summarize all data as a default option.
```{r}
mmetrics::add(df, metrics = metrics)
```

If we want `mmetrics::add()` to behave like `dplyr::mutate()` use `mmetrics::disaggregate()`.
```{r}
mmetrics::add(df, metrics = mmetrics::disaggregate(metrics), summarize = FALSE)
```


### Remove aggregate function from metrics using `mmetrics::disaggregate()`
It is hassle for users to re-define metrics when you would like to use these for `dplyr::mutate()`.
In this case, you can use `mmetrics::disaggregate()` to remove *the first aggregation function* for the argument and return disaggregated metrics.

```{r}
# Original metrics. sum() is used for this metrics
metrics
```

```{r}
# Disaggregate metrics!
metrics_disaggregated <- mmetrics::disaggregate(metrics)
# Woo! sum() are removed!!!
metrics_disaggregated
```

You can use these metrics with `dplyr::mutate()` for row-wise metrics computation.
```{r}
dplyr::mutate(df, !!!metrics_disaggregated)
```

...or, you can do the same compucation using `mmetrics::gmutate()` defind in our package.
In this case, you do not need to write `!!!` (bang-bang-bang) operator explicitly.
```{r}
mmetrics::gmutate(df, metrics = metrics_disaggregated)
```

## gmutate() and gsummarize()

`mmetrics::add()` is a just wrapper function for `mmetrics::gmutate()` and `mmetrics::gsummarize()`.
We can use these functions directly instead of `mmetrics::add()`.

```{r}
# Completely the same result with mmetrics::add(df, gender, metrics = metrics)
mmetrics::gsummarize(df, gender, metrics = metrics)
```


`metrics::gmutate()` is useful to calculate the metrics like "ratio in a group".
```{r}
# Cost ratio in each gender group
mmetrics::gmutate(df, gender, metrics = mmetrics::define(cost_ratio = cost/sum(cost)))
```


## Run multiple tabulations at once

If you would like to run code with multiple keys all at onece, you can use the combination of `!!(bangbang operator)` and `rlang::sym` as the following:

```{r}
# Define keys
keys <- c("gender", "age")
# Run
purrr::map(keys, ~ mmetrics::add(df, !!rlang::sym(.x), metrics = metrics))
```



